### 2016-04-07 CixPAG/paper58.Rmd
Update for Climatrans: precipitation and hot summer days

```{r}
rm(list=ls())
#xlim <- c(-10,40); ylim <- c(35,70)
xlim <- c(0,35); ylim <- c(45,70)
readecad <- FALSE
figshare=TRUE
nmin=50

@@

## Start the esd-library:
library(esd)
```

>>>>

```{r,echo=TRUE}
rm(list=ls())
#xlim <- c(-10,40); ylim <- c(35,70)
xlim <- c(0,35); ylim <- c(45,70)
readecad <- FALSE
figshare=TRUE
nmin=50

@@

## Start the esd-library:
library(esd)
## Information about the system and session
Sys.info()
sessionInfo()
```
